Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-13 bbbq_article.tex
Merged @fransbianchi's work into Results section of IEDB study

@@

Figure \ref{fig:2a} shows that there is a correlation between the
percentage of TMH-derived epitopes that is presented \emph{in vivo}
versus the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in a useful plot.

@@

From these findings, it is robustly predicted that
epitopes derived from TMHs are presented in both MHC-I and MHC-II.
See the supplementary Table \ref{tab:elution} for the exact values.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
  }
  \label{fig:elution_versus}
\end{figure}

>>>>

\frans{This section requires review}
\richel{This section requires review indeed}

@@

Figure \ref{fig:2a} shows that there is a correlation between the
percentage of TMH-derived epitopes that is presented \emph{in vivo}
versus the percentage of TMH-derived epitopes that is predicted to be presented
in MHC-I alleles. For MHC-II alleles, there were too few epitopes per MHC allele
to result in an informative figure.

@@

The percentage of TMH derived epitopes is lower than expected, 
for both the predictions \richel{Figure 1} 
and statistical chance \richel{indeed, need stats}, 
however these results are affected by 
(I) the probed proteins/peptides 
(II) the bias in mass spectrometry towards hydrophillic peptides (refs) and (III) availablilty of data for the different alleles.

In fact, these findings robustly confirm that
epitopes derived from human TMHs are presented in both MHC-I and MHC-II.
See the supplementary Table \ref{tab:elution} for the exact values.

We also mined the IEDB database for in
which T-cell responses were confirmed against specific human epitopes from the specified
alleles, from the total reports \richel{value}\% and \richel{value}\% concerned TMH-derived epitopes in MHC class I
and II, respectively 
(see Figure \ref{fig:t_cells_present_tmh_derived_epitopes}). 
This data confirms that not only TMH derived epitopes are presented on MHC, but also result in immune responses.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
  }
  \label{fig:t_cells_present_tmh_derived_epitopes}
\end{figure}
